Verb Meanings found in the ICB Corpus (top 200)

### 2022-01-26 prune/ICBEdataset_paper_InterCoderByLevels.Rmd
paper rmds

---
title: "Untitled"
output: html_document
---

```{r}
library(flextable)
library(tidyverse)
library(googlesheets4)

@@

icb_long_clean <- readRDS(file=paste0(here::here(), "/data/icb_long_clean.Rds")) #%>% 
                  #mutate(temp_row_id=paste(email_id, crisno,sentence_number_int_aligned, variable, sep="_")) %>%
                  #mutate(cleaned=temp_row_id %>% str_detect("_clean")) %>%
                  #mutate(temp_row_id= temp_row_id %>% str_replace("_clean","")) %>%
                  #arrange(desc(cleaned), temp_row_id) %>% 
                  #filter(!duplicated(temp_row_id)) %>%
                  #mutate(variable= variable %>% str_replace("_clean",""))

icb_wide_clean <- readRDS(file=paste0(here::here(), "/data/icb_wide_clean.Rds"))

@@

full_tree <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit?usp=sharing",
                                       sheet="Codebook in Tree Form")

>>>>

---
title: "ICBEdataset_paper_InterCoderByLevels"
output: html_document
---

```{r}
library(flextable)
library(tidyverse)
```

@@

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds")) #%>% 
                  #mutate(temp_row_id=paste(email_id, crisno,sentence_number_int_aligned, variable, sep="_")) %>%
                  #mutate(cleaned=temp_row_id %>% str_detect("_clean")) %>%
                  #mutate(temp_row_id= temp_row_id %>% str_replace("_clean","")) %>%
                  #arrange(desc(cleaned), temp_row_id) %>% 
                  #filter(!duplicated(temp_row_id)) %>%
                  #mutate(variable= variable %>% str_replace("_clean",""))

icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))

@@

target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview,_trees_sentences.xlsx")
full_tree    <- readxl::read_excel(target_file, sheet="Codebook in Tree Form")

### 2022-01-26 prune/ICBEdataset_paper_InternalValidity.Rmd
paper rmds

---
title: "InternalMeasurementValidity.Rmd"
output: html_document
---

@@

icb_long_clean <- readRDS(file=paste0(here::here(), "/data/icb_long_clean.Rds"))
icb_wide_clean <- readRDS(file=paste0(here::here(), "/data/icb_wide_clean.Rds"))

>>>>

---
title: "Internal Measurement Validity"
output: html_document
---

@@

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds"))
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))

### 2022-01-26 prune/ICBEdataset_paper_TableExampleSentenceCoding.Rmd
paper rmds

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(igraph)
p_load(tidyverse)
p_load(flextable)
p_load(ftExtra)
p_load(googlesheets4)
library(googlesheets4)

@@

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
sentence_example_sheet <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit?usp=sharing",
                                                    sheet="Sentence Tree Example Table")

>>>>

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(igraph)
p_load(tidyverse)
p_load(flextable)
p_load(ftExtra)

@@

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}

target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview,_trees_sentences.xlsx")
sentence_example_sheet    <- readxl::read_excel(target_file, sheet="Sentence Tree Example Table")

### 2022-01-26 prune/ICBEdataset_paper_TableSentenceExamples.Rmd
paper rmds

codings_long_agreement <- readRDS( paste0(here::here(), "ICBEdataset/data_out/codings_long_agreement.Rds")) 
codings_long_agreement_1_3 <- codings_long_agreement %>% filter(crisno==1 & sentence_number_int_aligned==3)
codings_long_agreement_2_11 <- codings_long_agreement %>% filter(crisno==2 & sentence_number_int_aligned==11)
codings_long_agreement_252_5 <- codings_long_agreement %>% filter(crisno==253 & sentence_number_int_aligned==5)
codings_long_agreement_209_3 <- codings_long_agreement %>% filter(crisno==209 & sentence_number_int_aligned==3)
codings_long_agreement_265_28 <- codings_long_agreement %>% filter(crisno==265 & sentence_number_int_aligned==28) #
codings_long_agreement_457_4 <- codings_long_agreement %>% filter(crisno==457 & sentence_number_int_aligned==4) #
codings_long_agreement_384_43 <- codings_long_agreement %>% filter(crisno==384 & sentence_number_int_aligned==43) #

#You have to rerun the embeddings too
codings_wide_agreed_embeded <- readRDS( paste0(here::here(), "ICBEdataset/data_out/codings_wide_agreed_embeded.Rds")) 
codings_wide_agreed_embeded_2_11 <- codings_wide_agreed_embeded %>% filter(crisno==2 & sentence_number_int_aligned==11)
codings_wide_agreed_embeded_265_28 <- codings_wide_agreed_embeded %>% filter(crisno==265 & sentence_number_int_aligned==28) #behavior is missing for one of them, do we want to call that degenerate?
codings_wide_agreed_embeded_384_43 <- codings_wide_agreed_embeded %>% filter(crisno==384 & sentence_number_int_aligned==43) #behavior is missing for one of them, do we want to call that degenerate?

@@

events_ft  %>% saveRDS(paste0(here::here(), "ICBEdataset/paper/tables/events_ft.Rds"))
events_ft

>>>>

codings_long_agreement <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreement.Rds")) 
codings_long_agreement_1_3 <- codings_long_agreement %>% filter(crisno==1 & sentence_number_int_aligned==3)
codings_long_agreement_2_11 <- codings_long_agreement %>% filter(crisno==2 & sentence_number_int_aligned==11)
codings_long_agreement_252_5 <- codings_long_agreement %>% filter(crisno==253 & sentence_number_int_aligned==5)
codings_long_agreement_209_3 <- codings_long_agreement %>% filter(crisno==209 & sentence_number_int_aligned==3)
codings_long_agreement_265_28 <- codings_long_agreement %>% filter(crisno==265 & sentence_number_int_aligned==28) #
codings_long_agreement_457_4 <- codings_long_agreement %>% filter(crisno==457 & sentence_number_int_aligned==4) #
codings_long_agreement_384_43 <- codings_long_agreement %>% filter(crisno==384 & sentence_number_int_aligned==43) #

#You have to rerun the embeddings too
codings_wide_agreed_embeded <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_wide_agreed_embeded.Rds")) 
codings_wide_agreed_embeded_2_11 <- codings_wide_agreed_embeded %>% filter(crisno==2 & sentence_number_int_aligned==11)
codings_wide_agreed_embeded_265_28 <- codings_wide_agreed_embeded %>% filter(crisno==265 & sentence_number_int_aligned==28) #behavior is missing for one of them, do we want to call that degenerate?
codings_wide_agreed_embeded_384_43 <- codings_wide_agreed_embeded %>% filter(crisno==384 & sentence_number_int_aligned==43) #behavior is missing for one of them, do we want to call that degenerate?

@@

events_ft  %>% saveRDS(paste0(here::here(), "/replication_paper/tables/events_ft.Rds"))
events_ft

### 2022-01-26 prune/ICBEdataset_paper_appendixPlayersandAgents.Rmd
paper rmds

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(tidyverse)
p_load(flextable)
p_load(ftExtra)
p_load(googlesheets4)
library(googlesheets4)

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, ft.arraystretch=0.75}
target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")

@@

actor_agents_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/actor_agents_ft.Rds'))
actor_agents_ft

>>>>

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(tidyverse)
p_load(flextable)
p_load(ftExtra)
```

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, ft.arraystretch=0.75}
target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")

@@

actor_agents_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/actor_agents_ft.Rds'))
actor_agents_ft

### 2022-01-26 prune/ICBEdataset_paper_appendixVerbCoarsened.Rmd
paper rmds

```{r}
icb_wide_clean <- readRDS(file=paste0(here::here(), "/data/icb_wide_clean.Rds"))
```

@@

  parsed %>% saveRDS(paste0(here::here(), "/data/parsed.Rds"))

  entities <- entity_extract(parsed, type = "all")
  entities %>% saveRDS(paste0(here::here(), "/data/entities.Rds"))

} else {
  parsed <- readRDS(paste0(here::here(), "/data/parsed.Rds"))
  entities <- readRDS(paste0(here::here(), "/data/entities.Rds"))

@@

target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")

@@

wordnet_rdf <- readRDS(paste0(here::here(), "/replication_data/in/wordnet_rdf.Rds") )

@@

#wordnet csv
filenames <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/") )
filepaths <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"), full.names = T)

@@

  #Isn't it just one minus the other?
  verbs_sentence_wordnet$distances <- rowSums((glosses_embeddings_expanded-sentences_embeddings_expanded)^2)
  verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds"))

@@

  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds") )

@@

first_two_hops_collapsed_ft  %>% saveRDS(here::here(), '/paper/tables/first_two_hops_collapsed_ft.Rds'))
first_two_hops_collapsed_ft

>>>>

```{r}
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))
```

@@

  parsed %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))

  entities <- entity_extract(parsed, type = "all")
  entities %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))

} else {
  parsed <- readRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))
  entities <- readRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))

@@

target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")

@@

wordnet_rdf <- readRDS(paste0(here::here(), "/replication_paper/in/wordnet_rdf.Rds") )

@@

#wordnet csv
filenames <- list.files(path=paste0(here::here(), "/replication_paper/data/in/wncsv-master/csv/") )
filepaths <- list.files(path=paste0(here::here(), "/replication_paper/data/in/wncsv-master/csv/"), full.names = T)

@@

  #Isn't it just one minus the other?
  verbs_sentence_wordnet$distances <- rowSums((glosses_embeddings_expanded-sentences_embeddings_expanded)^2)
  verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))

@@

  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds") )

@@

first_two_hops_collapsed_ft  %>% saveRDS(here::here(), '/replication_paper/tables/first_two_hops_collapsed_ft.Rds')
first_two_hops_collapsed_ft

### 2022-01-26 prune/ICBEdataset_paper_appendixVerbDomains.Rmd
paper rmds

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(tidyverse)
p_load(flextable)
p_load(ftExtra)
p_load(googlesheets4)
library(googlesheets4)

```{r}
icb_wide_clean <- readRDS(file=paste0(here::here(), "/data/icb_wide_clean.Rds"))
```

@@

wordnet_rdf <- readRDS(paste0(here::here(), "/replication_data/in/wordnet_rdf.Rds") )

@@

domains_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/domains_ft.Rds'))
domains_ft

>>>>

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(tidyverse)
p_load(flextable)
p_load(ftExtra)
```

```{r}
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))
```

@@

wordnet_rdf <- readRDS(paste0(here::here(), "/replication_paper/data/in/wordnet_rdf.Rds") )

@@

domains_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/domains_ft.Rds'))
domains_ft

### 2022-01-26 prune/ICBEdataset_paper_appendixVerbTrees.Rmd
paper rmds

fromsrcatch=F
if(fromsrcatch){
  #py$sentences
  #py$glosses
  sentences_embeddings <- py$sentences_embeddings
  glosses_embeddings <- py$glosses_embeddings

@@

  #Isn't it just one minus the other?
  verbs_sentence_wordnet$distances <- rowSums((glosses_embeddings_expanded-sentences_embeddings_expanded)^2)
  verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/data/verbs_sentence_wordnet.Rds"))

@@

  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/data/verbs_sentence_wordnet.Rds"))

@@

ggsave( filename=paste0(here::here(), "/paper/figures/hypernyms_plot.pdf"), plot=p, height=100,width =32,limitsize = FALSE)

@@

ggsave( filename=paste0(here::here(), "/paper/figures/hypernyms_rooted_plot.pdf"), plot=p_rooted, height=100,width =32,limitsize = FALSE)

>>>>

fromscratch=F
if(fromscratch){
  #py$sentences
  #py$glosses
  sentences_embeddings <- py$sentences_embeddings
  glosses_embeddings <- py$glosses_embeddings

@@

  #Isn't it just one minus the other?
  verbs_sentence_wordnet$distances <- rowSums((glosses_embeddings_expanded-sentences_embeddings_expanded)^2)
  verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))

@@

  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))

@@

ggsave( filename=paste0(here::here(), "/replication_paper/figures/hypernyms_plot.pdf"), plot=p, height=100,width =32,limitsize = FALSE)

@@

ggsave( filename=paste0(here::here(), "/replication_paper/figures/hypernyms_rooted_plot.pdf"), plot=p_rooted, height=100,width =32,limitsize = FALSE)

### 2022-01-26 prune/ICBEdataset_paper_uncertainty.Rmd
paper rmds

```{r}
library(flextable)
library(tidyverse)
library(googlesheets4)

@@

full_tree <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit?usp=sharing",
                                       sheet="Codebook in Tree Form")

@@

write_csv(codings_long_agreed, paste0(here::here(), "/data_out/codings_long_agreed.csv"))
write_csv(codings_wide_agreed, paste0(here::here(), "/data_out/codings_wide_agreed.csv"))

>>>>

```{r}
library(flextable)
library(tidyverse)

@@

```{r}
target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview,_trees_sentences.xlsx")
full_tree    <- readxl::read_excel(target_file, sheet="Codebook in Tree Form")

@@

# write_csv(codings_long_agreed, paste0(here::here(), "/data_out/codings_long_agreed.csv"))
# write_csv(codings_wide_agreed, paste0(here::here(), "/data_out/codings_wide_agreed.csv"))

### 2022-01-26 prune/ICBEdataset_paper_uncertainty_bayesian.Rmd
paper rmds

---
title: "Untitled"
output: html_document
---

@@

events_wide_i_event_count_thresholded %>% saveRDS(paste0(here::here(), '/data_temp/events_wide_i_event_count_thresholded.Rds'))

@@

library(tidyverse)
events_wide_i_event_count_thresholded <- readRDS(paste0(here::here(), '/data_temp/events_wide_i_event_count_thresholded.Rds'))

>>>>

---
title: "Uncertainty Bayesian"
output: html_document
---

@@

# events_wide_i_event_count_thresholded %>% saveRDS(paste0(here::here(), '/data_temp/events_wide_i_event_count_thresholded.Rds'))

@@

library(tidyverse)
# events_wide_i_event_count_thresholded <- readRDS(paste0(here::here(), '/data_temp/events_wide_i_event_count_thresholded.Rds'))

### 2022-01-26 replication_data/rmd/02_format_and_clean.rmd
paper rmds

Save icb_long_clean!
```{r}
saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_paper/data/input/icb_long_clean.Rds"))

@@

saveRDS(icb_wide_clean, paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds"))

>>>>

Save icb_long_clean!
```{r}
saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds"))

@@

saveRDS(icb_wide_clean, paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds")) 
saveRDS(icb_wide_clean, paste0(here::here(), "/replication_paper/in/icb_wide_clean.Rds"))

### 2022-01-26 replication_paper/rmd/ICBEdataset_paper_PlotInterCoderAgreement.Rmd
paper rmds

---
title: 'Intercoder Agreement'
site: bookdown::bookdown_site
bibliography: ../ICBintro.bib
output: 
  rticles::arxiv_article:
    keep_tex: true
header-includes:
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
  - \usepackage{natbib} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage[capposition=top]{floatrow}
  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
---

@@

```{r}
library(flextable)
library(tidyverse)
library(googlesheets4)

```{r}
icb_long_clean <- readRDS(file=paste0(here::here(), "/data/icb_long_clean.Rds"))

codings_long <- readRDS(paste0(here::here(), '/data_out/codings_long.Rds'))
codings_long_agreement <- readRDS( paste0(here::here(), '/data_out/codings_long_agreement.Rds'))
codings_long_agreed <- readRDS( paste0(here::here(), '/data_out/codings_long_agreed.Rds'))
codings_wide_agreed <- readRDS( paste0(here::here(), '/data_out/codings_wide_agreed.Rds'))

@@

confidence_totals <- bind_rows(
  icb_long_clean %>% filter(email_id %>% str_detect('expert') & variable_normalized=='raterconfidence' ) %>% count(value_normalized) %>% mutate(coder="expert") %>% mutate(n= (n/sum(n)*100) %>% round(1) %>% paste0("%") ),
  icb_long_clean %>% filter(email_id %>% str_detect('undergrad') & variable_normalized=='raterconfidence' ) %>% count(value_normalized)  %>% mutate(coder="undergrad") %>% mutate(n=(n/sum(n)*100) %>% round(1) %>% paste0("%"))
) %>%
  mutate(confidence=value_normalized %>% factor(levels=c('none','low','high','complete')) %>% as.numeric() ) %>%
  mutate(x=0.05)

@@

p_percent_chose_tag_by_concept %>% saveRDS(paste0(here::here(), '/paper/figures/p_percent_chose_tag_by_concept.Rds'))
p_percent_chose_tag_by_concept

ggplot2::ggsave(file=paste0(here::here(), '/paper/figures/p_percent_chose_tag_by_concept.png'), 
                plot = p_percent_chose_tag_by_concept, width=8, height=6)
#table(expert_majority=codings_long$expert_majority,
#      undergrad_majority=codings_long$undergrad_majority)

>>>>

---
title: 'Plot Intercoder Agreement'
site: bookdown::bookdown_site
bibliography: ../ICBintro.bib
output: 
  rticles::arxiv_article:
    keep_tex: true
header-includes:
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
  - \usepackage{natbib} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage[capposition=top]{floatrow}
  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
---

@@

```{r}
library(flextable)
library(tidyverse)
```

```{r}
icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/data/in/icb_long_clean.Rds")) 
codings_long <- readRDS(paste0(here::here(), '/replication_data/data/in/codings_long.Rds'))
codings_long_agreement <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_long_agreement.Rds'))
codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_long_agreed.Rds'))
codings_wide_agreed <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_wide_agreed.Rds'))

@@

```{r}
confidence_totals <- bind_rows(
  icb_long_clean %>% filter(email_id %>% str_detect('expert') & variable_normalized=='raterconfidence' ) %>% count(value_normalized) %>% mutate(coder="expert") %>% mutate(n= (n/sum(n)*100) %>% round(1) %>% paste0("%") ),
  icb_long_clean %>% filter(email_id %>% str_detect('undergrad') & variable_normalized=='raterconfidence' ) %>% count(value_normalized)  %>% mutate(coder="undergrad") %>% mutate(n=(n/sum(n)*100) %>% round(1) %>% paste0("%"))
) %>%
  mutate(confidence=value_normalized %>% factor(levels=c('none','low','high','complete')) %>% as.numeric() ) %>%
  mutate(x=0.05)

@@

p_percent_chose_tag_by_concept %>% saveRDS(paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_concept.Rds'))
p_percent_chose_tag_by_concept

ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_concept.png'), 
                plot = p_percent_chose_tag_by_concept, width=8, height=6)
#table(expert_majority=codings_long$expert_majority,
#      undergrad_majority=codings_long$undergrad_majority)

### 2022-01-26 replication_paper/rmd/ICBEdataset_paper_appendixVerbMeanings.Rmd
paper rmds

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(igraph)
p_load(tidyverse)
p_load(flextable)
p_load(ftExtra)
p_load(googlesheets4)
library(googlesheets4)

```{r}
icb_wide_clean <- readRDS(file=paste0(here::here(), "/data/icb_wide_clean.Rds"))
```

@@

target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")

@@

#wordnet csv
filenames <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"))
filepaths <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"), full.names = T)

@@

  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds"))

@@

ggsave(filename=paste0(here::here(), "/paper/figures/hypernyms_plot.pdf"), plot=p, height=100,width =32,limitsize = FALSE)

@@

ggsave(filename=paste0(here::here(), "/paper/figures/hypernyms_rooted_plot.pdf"), plot=p_rooted, height=100,width =32,limitsize = FALSE)

@@

verbs_sentence_wordnet_top_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/verbs_sentence_wordnet_top_ft.Rds'))
verbs_sentence_wordnet_top_ft

>>>>

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(igraph)
p_load(tidyverse)
p_load(flextable)
p_load(ftExtra)
```

```{r}
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))
```

@@

target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")

@@

#wordnet csv
filenames <- list.files(path=paste0(here::here(), "/replication_paper/data/in/wncsv-master/csv/"))
filepaths <- list.files(path=paste0(here::here(), "/replication_paper/data/in/wncsv-master/csv/"), full.names = T)

@@

  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))

@@

ggsave(filename=paste0(here::here(), "/replication_paper/figures/hypernyms_plot.pdf"), plot=p, height=100,width =32,limitsize = FALSE)

@@

ggsave(filename=paste0(here::here(), "/replication_paper/figures/hypernyms_rooted_plot.pdf"), plot=p_rooted, height=100,width =32,limitsize = FALSE)

@@

verbs_sentence_wordnet_top_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/verbs_sentence_wordnet_top_ft.Rds'))
verbs_sentence_wordnet_top_ft
